Democracy, Public Support, and Measurement Uncertainty

### 2021-08-02 paper/dcpo_demsupport.Rmd
adjust disucssion on results.  @sammo3182 Table 2and 3 might need relable for variables. please check.

We proceed in three steps.
First, we reproduce the original analyses of Claassen [-@Claassen2020a; -@Claassen2020b], which included only the point estimates of the latent variable of democratic support and so exclude its measurement uncertainty.
Second, we collect the original cross-national survey data, replicate the latent variable measure of democratic support used in the two articles, and conduct the articles' analyses again, this time maintaining the entire distribution of estimates of democratic support in each country-year.
As the third step, we collect even more survey data---increasing these source data by one-fourth---and re-estimate the two articles' analyses once more, again maintaining the full distribution of estimates to preserve measurement uncertainty.

## Data Recollection and Incorporating Uncertainty
When we recollected the original data, we could not entirely achieve a primary replication [see @Grossman2020, p. 18] based @Claassen2020a's Dataverse materials.
It turned out that we have differences in number of country-year surveys and in sample size.
Specificially, our replication data has five fewer observations, three of which are no longer available in originial survey data and 2 seem to have never existed, and one more survey item which was conflated in original data [See more detail in Appendix].

@@

Following this line, after replicating the original analyses with point estimates, we incorportate uncertainty in analysis model using our replication data.
We take the distribution of the latent (explanatory) variable, the outcome variable, and control variables to account for the uncertainty from the measurement model as well as outcome and control variables.
We take 900 draws from the distribution of public democratic support, duplicate each article's analysis dataset of variables without "measurement error" 900 times, and assign them to each a different random draw from the posterior distribution of democracy indices.
We estimate each analysis model repeatedly on its respective collection of the datasets, and then make inferences from the distribution of parameter estimates by accounting for both within model standard error and between model variance.
This combine rule was set out in @Rubin1987, and has been employed in research of measurement errors [see, e.g., @Schnakenberg2014; @Crabtree2015] as well as incorporated in @Blackwell2017a's multiple overimputation (MO) to handle missing values and measurement uncertainty.
We also employ one alternative technique known as "method of composition" (MOC)  [@Treier2008, p. 215] as a robustness check [see Online Supplementary Material \@ref(moc)].

@@

<!-- This paragraph should be revised. -->
We also expanded Claassen's data pool assembling as much data on democratic support as possible from available opinion surveys around the world. 
The expansion ended with `r dcpo_input_ncyi` national opinions on democracy from `r dcpo_input_surv` national surveys, representing a `r increase_cyi`% and `r increase_surv`% increase respectively over the `r supdem_ncy` opinions and `r supdem_surv` national surveys used in Claassen [-@Claassen2020a; -@Claassen2020b].^[These figures represent the survey data actually used in estimating public support for democracy; as in Claassen [-@Claassen2020a; -@Claassen2020b], countries for which two separate years of survey data were not available were excluded.]

Besides accounting for uncertainty in latent variable estimates, we also included the measurement uncertainty in democracy indices and corruption index [See Appendix].

@@

Figure \@ref(fig:plot-mainAJPS) presents the reanalyses of the hypothesis that public support influences the level of democracy, with democratic support pooled for all countries [@Claassen2020a, Model 1] in the left panel and separated by regime type (Model 2) on the right.
The uppermost set of results replicate @Claassen2020a without uncertainty.
The middle results introduce the uncertainty in the measurement of public support into the model.
And the lowermost set presents the results estimated with the expanded data.

In comparison to the original result, the positive coefficients for democratic support in both model accounting for the uncertainty are no longer statistically significant.
This result is robust when using separated regime types in the explanatory variable. 
Nor do applying system GMM models and using alternative methods for uncertainty incorporation methods alters the conclusion (see Online Supplementary Material \@ref(fullAJPS), \@ref(fullAPSR), and \@ref(moc)).

@@

The importance of accounting for the measurement uncertainty appear more evident when the relevant variable plays as the outcome variable. 
In Figure \@ref(fig:plot-mainAPSR), we examine the thermostatic model of democratic support per @Claassen2020b [p. 47, Models 1.1 and 1.2]. 
When the uncertainty is ignored, the coefficient of $\Delta$liberal democracy (the uppermost set), the yearly changes of the institutional feature is negative inferring that democratic mood decreases as democracy increases and vice versa. 
However, when the measurement uncertainty is properly accounted (the middle set), the point estimate shifts towards zero and the coefficient is no longer significant.
More data (the lowermost set), again, only adjusts the confidence intervals but not direction nor significance.

@@

In short, the conclusions of Claassen [-@Claassen2020a; -@Claassen2020b] that public support has a positive effect on democracy and democracy a negative effect on support are not empirically supported once measurement uncertainty is taken into account, even when more data are used.

There are several potential methodological explanations for these null results.
One issue is that the survey items employed---which ask respondents to assess the desirability or appropriateness of democracy, to compare democracy to some undemocratic alternative, or to assess one of these alternatives---may not capture every aspect of democratic support necessary for it to play its hypothesized roles in the classic theory.
If only those who profess to prefer democracy to its alternatives _and also_ value freedom of expression, freedom of association, and pluralism of opinion will take appropriate action when democracy is threatened, then this measure is inadequate to its purpose [see, e.g., @Schedler2007].
Moreover, given the multi-faceted nature of democratic attitudes, even the inclusion of such questions in unidimensional public opinion models such as those provided by @Claassen2019 or @Solt2020a are unlikely to be sufficient [see, e.g., @Wuttke2020].
Another issue is that even if these survey questions do capture support for the generic concept of democracy, these measurement models might still be incapable of suitably capturing democratic support due to the variation in understanding the concept across countries or over time within countries [@Wuttke2021]. 
Yet another is that this measure provides no assessment of the _relative_ importance the public affords democracy.
It provides no information on the extent to which other values, such as policy preferences or partisanship, weigh more heavily---and there is growing evidence that, at least in the United States, there are many for whom these other considerations excuse substantial transgressions against democracy [see @bartels_ethnic_2020; @Carey2020; @graham_democracy_2020; @McCoy2020].

There are theoretical explanations for the null results as well.
With regard to how levels of democracy affect public support, we note that even the proponents of the classic argument did not contend that the mere existence of democratic institutions, no matter how consistently feckless and ineffective, would generate support among the public: instead, they maintained, public support would be gained through experience with government performance that was generally effective [@lipset_social_1959, 86-89; @Easton1965, 119-120].
There is some empirical support for this, with government effectiveness positively related to public support among democracies and negatively related in non-democracies [@Magalhaes2014]. 
The finding of @Krieckhaus2014 that income inequality is strongly negatively related to public support in democracies suggests that performance regarding redistribution is particularly important.
Relatedly, on the reverse part of the classic argument, @Qi2011 suggests that democratic support alone cannot be expected to generate democratic change and oppose backsliding.
Instead, that work contends, it is the combination of democratic support and dissatisfaction with current regime performance that generates demand for greater democracy.
The effects of public support also have cultural-bound.
@Brunkert2019 contends outspoken support for democracy is a "deceptive indicator of public's affinity to democracy" [423] and finds public support has neither pro-democratic nor anti-authoritarian effect without controlling emancipative values.
Empirical results show that the meaning of support for democracy is dependent on emancipation values and is reversed to its own negation in a society with weak emancipative values [see, e.g.,@Kirsch2019, 83-85].
And we must be open to the possibility that no theoretical elaboration, no respecification of these models will reveal relationships between public opinion and democracy.
Democratic backsliding may simply be primarily a matter of elite decisionmaking [see, e.g., @levitsky_how_2018].
Regardless, these explanations indicate that there remains much work to be done in the empirical study of public support and democracy.

@@

In this letter, we reexamined the findings from Claassen [-@Claassen2020a; -@Claassen2020b], two articles that maintain that public support helps the survival of democracy and democratic development has a thermostatic effect on public support.
We demonstrated the importance of incorporating measurement uncertainty in analyzing the relationship between public support and democracy.
Taking uncertainty into account rendered both articles' conclusions without empirical support, even when we added considerable more data.

@@

The null results reached in this letter could arise from several sources.
We identified a number of potential shortcomings in the measurement of democratic support and ways in which the analysis models might be underspecified.
All of these could and should be explored in future research, though there are also theoretically grounded reasons to suspect that the relationships are in fact negligible.
In any event, the sanguine assessment that readers may draw from Claassen [-@Claassen2020a; -@Claassen2020b]---that the fate of democracies depend on public support, and when eroded, their publics will rally to them---is not supported by the current evidence.
Those who would defend democracy have no grounds to be complacent.

>>>>

We proceed in three steps.
First, we reproduce the original analyses of Claassen [-@Claassen2020a; -@Claassen2020b], which included only the point estimates of the latent variable of democratic support and so exclude its measurement uncertainty.
Second, we collect the original cross-national survey data, replicate the latent variable measure of democratic support used in the two articles, and conduct the articles' analyses again, this time maintaining the entire distribution of estimates of democratic support in each country-year.
As the third step, we collect even more survey data---increasing these source data by one-third---and re-estimate the two articles' analyses once more, again maintaining the full distribution of estimates to preserve measurement uncertainty.

## Data Recollection and Incorporating Uncertainty
Despite the great effort of collecting data and identifying differences, we could not entirely achieve a primary replication [see @Grossman2020, p. 18] based on @Claassen2020a's Dataverse materials.
Our replication data has differences in number of country-year surveys and in sample size.
Specificially, we have five fewer observations, three of which are no longer available in originial survey data and two seem to have never existed, and one more survey item which was conflated in original data [see Online Supplementary Material].

@@

Following this line, after replicating the original analyses with point estimates, we incorportate uncertainty in analysis models using our replication data.
We take the distribution of the latent (explanatory) variable, the outcome variable, and control variables to account for the uncertainty.
We take 900 draws from the posterior distribution of democratic support, outcome, and control variables with errors.
We then duplicate each article's analysis dataset of variables "without" measurement error 900 times, and assign them to each a different random draw from the distributions of variables with measurement error. 
We estimate each analysis model repeatedly on its respective collection of the datasets, and then make inferences from the distribution of parameter estimates by accounting for both within model standard error and between model variance.
This combine rule was set out in @Rubin1987, and has been employed in research of measurement errors [see, e.g., @Schnakenberg2014; @Crabtree2015] as well as incorporated in @Blackwell2017a's multiple overimputation (MO) to handle missing values and measurement uncertainty.
We also employ one alternative technique known as "method of composition" (MOC)  [@Treier2008, p. 215] as a robustness check [see Online Supplementary Material \@ref(moc)].

@@

We also expanded Claassen's data pool assembling as much data on democratic support as possible from available opinion surveys around the world. 
The expansion ended with `r dcpo_input_ncyi` national opinions on democracy from `r dcpo_input_surv` national surveys, representing a `r increase_cyi`% and `r increase_surv`% increase respectively over the `r supdem_ncy` opinions and `r supdem_surv` national surveys used in Claassen [-@Claassen2020a; -@Claassen2020b].^[These figures represent the survey data actually used in estimating public support for democracy; as in Claassen [-@Claassen2020a; -@Claassen2020b], countries for which two separate years of survey data were not available were excluded.]

@@

Figure \@ref(fig:plot-mainAJPS) presents the reanalyses of the hypothesis that public support influences the level of democracy, with democratic support pooled for all countries [@Claassen2020a, Model 1] in the left panel and separated by regime type (Model 2) on the right.
The uppermost set of results replicate @Claassen2020a without uncertainty.
The middle results introduce the uncertainty in the measurement of public support and democratic indices into the model.
And the lowermost set presents the results estimated with the expanded data with uncertainty.

In comparison to the original result, the positive coefficients for democratic support in both models accounting for the uncertainty are no longer statistically significant.
This result is robust when using separated regime types in the explanatory variable. 
Nor do applying system GMM models and using alternative method for uncertainty incorporation alters the conclusion (see Online Supplementary Material \@ref(fullAJPS), \@ref(fullAPSR), and \@ref(moc)).

@@

The importance of accounting for the measurement uncertainty appear more evident when the relevant variable plays as the outcome variable. 
In Figure \@ref(fig:plot-mainAPSR), we examine the thermostatic model of democratic support per @Claassen2020b [p. 47, Models 1.1 and 1.2]. 
When the uncertainty is ignored, the coefficient of $\Delta$liberal democracy (the uppermost set), the yearly changes of the institutional feature is negative inferring that the change in democratic mood decreases as change in democracy increases and vice versa. 
However, when the measurement uncertainty is properly accounted (the middle set), the point estimate shifts towards zero and the coefficient is no longer significant.
More data (the lowermost set), again, only adjusts the confidence intervals but not direction nor significance.

@@

In short, the conclusions of Claassen [-@Claassen2020a; -@Claassen2020b] that public support has a positive effect on democracy and change in democracy a negative effect on change in support are not empirically supported once measurement uncertainty is taken into account, even when more data are used.

There are theoretical explanations for the null results.
With regard to how levels of democracy affect public support, we note that even the proponents of the classic argument did not contend that the mere existence of democratic institutions, no matter how consistently feckless and ineffective, would generate support among the public: instead, they maintained, public support would be gained through experience with government performance that was generally effective [@lipset_social_1959, 86-89; @Easton1965, 119-120].
There is some empirical support for this, with government effectiveness positively related to public support among democracies and negatively related in non-democracies [@Magalhaes2014]. 
The finding of @Krieckhaus2014 that income inequality is strongly negatively related to public support in democracies suggests that performance regarding redistribution is particularly important.
Relatedly, on the reverse part of the classic argument, @Qi2011 suggests that democratic support alone cannot be expected to generate democratic change and oppose backsliding.
Instead, that work contends, it is the combination of democratic support and dissatisfaction with current regime performance that generates demand for greater democracy.
The effects of public support also have cultural-bound.
@Brunkert2019 contends outspoken support for democracy is a "deceptive indicator of public's affinity to democracy" [423] and finds public support has neither pro-democratic nor anti-authoritarian effect without controlling emancipative values.
Empirical results show that the meaning of support for democracy is dependent on emancipation values and is reversed to its own negation in a society with weak emancipative values [see, e.g.,@Kirsch2019, 83-85].
And we must be open to the possibility that no theoretical elaboration, no respecification of these models will reveal relationships between public opinion and democracy.
Democratic backsliding may simply be primarily a matter of elite decisionmaking [see, e.g., @levitsky_how_2018].

There are several potential methodological explanations for these null results as well.
One issue is that the survey items employed---which ask respondents to assess the desirability or appropriateness of democracy, to compare democracy to some undemocratic alternative, or to assess one of these alternatives---may not capture every aspect of democratic support necessary for it to play its hypothesized roles in the classic theory.
If only those who profess to prefer democracy to its alternatives _and also_ value freedom of expression, freedom of association, and pluralism of opinion will take appropriate action when democracy is threatened, then this measure is inadequate to its purpose [see, e.g., @Schedler2007].
Moreover, given the multi-faceted nature of democratic attitudes, even the inclusion of such questions in unidimensional public opinion models such as those provided by @Claassen2019 or @Solt2020a are unlikely to be sufficient [see, e.g., @Wuttke2020].
Another issue is that even if these survey questions do capture support for the generic concept of democracy, these measurement models might still be incapable of suitably capturing democratic support due to the variation in understanding the concept across countries or over time within countries [@Wuttke2021]. 
Yet another is that this measure provides no assessment of the _relative_ importance the public affords democracy.
It provides no information on the extent to which other values, such as policy preferences or partisanship, weigh more heavily---and there is growing evidence that, at least in the United States, there are many for whom these other considerations excuse substantial transgressions against democracy [see @bartels_ethnic_2020; @Carey2020; @graham_democracy_2020; @McCoy2020]. 
Regardless, these explanations indicate that there remains much work to be done in the empirical study of public support and democracy.

@@

In this letter, we reexamine the findings from Claassen [-@Claassen2020a; -@Claassen2020b], two articles that maintain that public support helps the survival of democracy and democratic development has a thermostatic effect on public support.
We demonstrate the importance of incorporating measurement uncertainty in analyzing the relationship between public support and democracy.
Taking uncertainty into account rendered both articles' conclusions without empirical support, even when we added considerable more data.

@@

The null results reached in this letter could arise from several sources.
There are theoretically grounded reasons of government effectiveness, democratic understanding, and generical-or-behavioral support to suspect that the relationships are in fact negligible.
We also identified a number of potential shortcomings in the measurement of democratic support and ways in which the analysis models might be underspecified.
All of these could and should be explored in future research.
In any event, the sanguine assessment that readers may draw from Claassen [-@Claassen2020a; -@Claassen2020b]---that the fate of democracies depend on public support, and when eroded, their publics will rally to them---is not supported by the current evidence.
Those who would defend democracy have no grounds to be complacent.
